### 2022-07-11 src/text/1-introduction.tex
Update introduction

Very high energy cosmic gamma-ray reaching Earth interact in the atmosphere and
create a large shower of secondary particles that can be observed from the ground.
Ground-based gamma-ray astronomy relies on this phenomenon to detect the
primary gamma-ray photons and measure their direction and energy.
It covers the energy range from fews tens of GeV up to the PeV.
Two main instrument categories exist. Imaging Atmospheric Cherenkov
Telescopes (IACT) make images of atmospheric showers by detecting the Cherenkov radiation
emitted by the cascading charged particles and use these images to reconstruct
the properties of the incident particle.

@@

The Cherenkov Telescope Array (CTA) will be operated as an open observatory for
the first time. Thus there is a need for open analysis software as well.

>>>>

Very high energy cosmic gamma-ray reaching Earth interact in the atmosphere and
create a large shower of secondary particles that can be observed from the ground.
Ground-based gamma-ray astronomy relies on this phenomenon to detect the
primary gamma-ray photons and measure their direction and energy.
It covers the energy range from fews tens of GeV up to the PeV.
Two main instrument categories exist \citep{2015CRPhy..16..610D}.
Imaging Atmospheric Cherenkov Telescopes (IACT) make images of atmospheric showers
by detecting the Cherenkov radiation emitted by the cascading charged particles and
use these images to reconstruct the properties of the incident particle.

@@

The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
as an open observatory in the domain. Its data will be shared Thus there is a need for open analysis software as well.
